### 2022-11-11 NSF2022/Description/backgroundv2.tex
wrapped up first draft of SA2

The key idea is to define the dynamics using the following boundary
value problem system:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && \xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  &&\quad \xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase stresses, respectively; $I$ is the
$n\times n$ identity matrix. For vectors $\aa, \bb \in \mathbb{R}^2$,
we follow the usual convention of defining the ``cross product'' as $\aa
\times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.

@@

The solution of the PDEs~\eqref{eqn:stokes} and~\eqref{eqn:phse} is
challenging because of the complex and unbounded domain. Even more
troubling is when dense suspensions are considered. Integral equation
methods offer an alternative formulation of the PDEs that only require
meshing the boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a IE formulation
includes a discretization that is high-order, or even spectrally,
accurate; results in a well-conditioned linear system that can be solved
iteratively with a mesh-independent number of iterations of a Krylov
method such as the generalized minimal residual method (GMRES). However,
IEs do have several challenges: nearly touching granules requires a
quadrature rule for nearly-singular integrals; their discretization
results in dense matrices; and they cannot immediately be applied to
non-linear PDEs. The IE community, including PI Quaife, has developed a
variety of tools to address these numerical challenges, and we discuss
our planned approach in Section~\ref{sec:specificaim2}.

@@

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored in the phase transitions. Mathematically,
the energy law states that changes in granule configuration
instantaneously change the phase energy $E$. The dynamics are such that
the change energy is lost due to hydrodynamic dissipation. Further
details and generalizations are provided in \S\ref{sec:specific_aim1}
and \S\ref{sec:specific_aim_3}. Because $E$ depends both on $\phi$ and
$\Omega(t)$, the derivation of~\eqref{eq:energy_law} is somewhat subtle
and has been worked out in detail in~\cite{Fu2018_SIAM}. The
calculation uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux involving the phase stress
$T_i$ on the boundary, and a bulk term involving the Euler-Lagrange
derivative of $E$. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.

>>>>

The key idea is to define the dynamics using the following boundary
value problem system:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase stresses, respectively; $I$ is the
$n\times n$ identity matrix. For vectors $\aa, \bb \in \mathbb{R}^2$,
we follow the usual convention of defining the ``cross product'' as $\aa
\times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.

@@

@@

Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of the complex
and unbounded domain. This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss our planned approach in
Section~\ref{sec:specificaim2}.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored in the phase transitions. Mathematically,
the energy law states that changes in granule configuration
instantaneously change the phase energy $E$. The dynamics are such that
the change energy is lost due to hydrodynamic dissipation. Further
details and generalizations are provided in \S\ref{sec:specific_aim1}
and \S\ref{subsec:specific_aim_3}. Because $E$ depends both on $\phi$
and $\Omega(t)$, the derivation of~\eqref{eq:energy_law} is somewhat
subtle and has been worked out in detail in~\cite{Fu2018_SIAM}. The
calculation uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux involving the phase stress
$T_i$ on the boundary, and a bulk term involving the Euler-Lagrange
derivative of $E$. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
